---
title: ""
---

```{r}
#| echo: false
library(ggplot2)
library(htmltools)

tags$p("
       RwandaMarket was founded in 2024 by a team of entrepreneurs passionate about East African trade and technological innovation. The idea was born from recognizing the untapped potential of connecting Rwandan artisans with the growing Kenyan market, all while leveraging cutting-edge data science to optimize operations.")

library(ggplot2)

timeline_data <- data.frame(
  Year = c(2022, 2023, 2024, 2024, 2024, 2025),
  Event = c("Data Science \n Sole proprietorship", "Data Science \n Limited Company", "RwandaMarket \n Concept Development", "Physical Store", "E-commerce", "B2B Services"),
  Milestone = c(1, 2, 3, 6, 7, 8)
)

ggplot(timeline_data, aes(x = Year, y = Milestone, label = Event)) +
  geom_point(color = "#7C4700", size = 5) +
  geom_text(vjust = -1, hjust = 0.5, size = 3.5) +
  theme_minimal() +
  labs(title = "RwandaMarket Company Timeline", x = "Year", y = "") +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank()) +
  scale_x_continuous(limits = c(2021, 2026), breaks = 2021:2026) +
  scale_y_continuous(limits = c(0, 11))

```

### Legal Structure and Ownership

```{r}
#| echo: false
library(ggplot2)

tags$p("RwandaMarket is a product of Kwiz Computing Techonologies Limited, a registered Private Company (limited by shares) in Kenya. The company's ownership is distributed as follows:")

shareholders <- data.frame(
  Name = c("Kwizera Jean Victor", "Iragena Vincent de Paul"),
  Role = c("Active Cofounder", "Cofounder"),
  Shares = c(2000, 1000),
  Percentage = c("66.7%", "33.3%")
)

shareholders |> knitr::kable(caption = "Kwiz Computing Technologies Limited - Shareholding")
```

### Location and Facilities


```{r}
#| echo: false
tags$h4("Headquarters")
tags$p("Our main office will be located in the heart of Nairobi's business district:")
tags$p("[PLACEHOLDER: Exact address]")
tags$p("This central location will allow us to easily connect with our customers, partners, and the broader business community.")
```

```{r}
#| echo: false
tags$h4("Flagship Store")
tags$p("Our physical retail presence will be anchored by our flagship store:")
tags$p("[PLACEHOLDER: Exact address]")
tags$p("This store will showcase our full range of Rwandan products and serves as a cultural hub for events and workshops.")
```

```{r}
#| echo: false
tags$h4("Warehouse and Distribution Center")
tags$p("To ensure efficient order fulfillment and inventory management, we will operate a state-of-the-art warehouse:")
tags$p("[PLACEHOLDER: Exact address]")
tags$p("This facility will be equipped with advanced inventory tracking systems and optimized for quick order processing and shipping.")
```


### Core Values

1. **Cultural Appreciation**: We celebrate and promote Rwandan culture and craftsmanship.
2. **Technological Innovation**: We leverage cutting-edge technology to enhance all aspects of our business.
3. **Ethical Trade**: We ensure fair compensation and sustainable practices throughout our supply chain.
4. **Customer-Centricity**: We prioritize customer satisfaction in both our B2C and B2B operations.
5. **Continuous Learning**: We constantly seek to improve and adapt to changing market conditions.

```{r}
#| echo: false

tags$br()
tags$p("RwandaMarket stands at the intersection of tradition and innovation, bringing the best of Rwanda to Kenya while setting new standards for cross-border e-commerce in East Africa.")
```
