---
title: "Contact Us"
---

We value open communication with our customers, partners, and stakeholders. Whether you have a question about our products, want to explore B2B opportunities, or are interested in joining our team, we're here to help.

## Contact Information

- **General Inquiries**: info@rwandamarket.com
- **Customer Support**: support@rwandamarket.com
- **B2B Solutions**: b2b@rwandamarket.com
- **Careers**: careers@rwandamarket.com
- **Press and Media**: media@rwandamarket.com

**Phone**: +254 20 [PLACEHOLDER: Phone number]

**Physical Address**:  
RwandaMarket Ltd.  
[PLACEHOLDER: Street Address]  
Nairobi, Kenya

**Operating Hours**:  
Monday - Friday: 9:00 AM - 6:00 PM (EAT)  
Saturday: 10:00 AM - 4:00 PM (EAT)  
Sunday: Closed

## Contact Form

```{r echo=FALSE}
library(shiny)

ui <- fluidPage(
  textInput("name", "Name:"),
  textInput("email", "Email:"),
  selectInput("subject", "Subject:", 
              choices = c("General Inquiry", "Product Question", "B2B Opportunities", "Feedback", "Other")),
  textAreaInput("message", "Message:"),
  actionButton("submit", "Submit")
)

server <- function(input, output) {
  observeEvent(input$submit, {
    # In a real application, this would send the form data to a server
    print(paste("Form submitted by", input$name))
  })
}

shinyApp(ui, server)
```

## Connect With Us

Stay updated with our latest products, offers, and company news by following us on social media:

- Facebook: [/RwandaMarket](https://www.facebook.com)
- Instagram: [@RwandaMarket](https://www.instagram.com)
- Twitter: [@RwandaMarket_KE](https://www.twitter.com)
- LinkedIn: [RwandaMarket Ltd.](https://www.linkedin.com)

## Visit Our Store

Experience our products firsthand at our flagship store in Nairobi:

[PLACEHOLDER: Store Address]

```{r echo=FALSE}
library(leaflet)

leaflet() %>%
  addTiles() %>%
  setView(lng = 36.8219, lat = -1.2921, zoom = 13) %>%
  addMarkers(lng = 36.8219, lat = -1.2921, popup = "RwandaMarket Flagship Store")
```

## Feedback

Your feedback is crucial in helping us improve our services. If you have any suggestions or concerns, please don't hesitate to reach out. We appreciate your input and are committed to continuously enhancing your experience with RwandaMarket.

Thank you for your interest in RwandaMarket. We look forward to hearing from you and serving your needs for authentic Rwandan products and innovative B2B solutions.


