---
title: ""
execute: 
  echo: false
filters: 
  - shinylive
---

To fully leverage the benefits of free trade agreements, particularly within the East African Community (EAC), RwandaMarket will implement a comprehensive system for tracking, documenting, and analyzing our use of these benefits.

## Free Trade Benefit Forms

### 1. Product Origin Declaration Form

```{shinylive-r}
#| standalone: TRUE
library(shiny)

ui <- fluidPage(
bslib::card(
  textInput("product_name", "Product Name"),
    textInput("hs_code", "HS Code"),
    selectInput("country_of_origin", "Country of Origin", 
                choices = c("Rwanda", "Kenya", "Uganda", "Tanzania", "Burundi", "South Sudan")),
    numericInput("local_content_percentage", "Percentage of Local Content", value = 0, min = 0, max = 100),
    textAreaInput("manufacturing_process", "Brief Description of Manufacturing Process"),
    checkboxInput("meets_origin_criteria", "Meets EAC Rules of Origin Criteria"),
    fileInput("supporting_documents", "Upload Supporting Documents", multiple = TRUE)
))

server = function(ui, server) {
  
}

shinyApp(ui, server)
```

### 2. Tariff Savings Tracking Form

```{shinylive-r}
#| standalone: TRUE

ui <- fluidPage(
bslib::card(
  textInput("product_name", "Product Name"),
  textInput("hs_code", "HS Code"),
  selectInput("origin_country", "Origin Country", 
              choices = c("Rwanda", "Kenya", "Uganda", "Tanzania", "Burundi", "South Sudan")),
  selectInput("destination_country", "Destination Country", 
              choices = c("Rwanda", "Kenya", "Uganda", "Tanzania", "Burundi", "South Sudan")),
  numericInput("shipment_value", "Shipment Value (USD)", value = 0),
  numericInput("standard_tariff_rate", "Standard Tariff Rate (%)", value = 0),
  numericInput("preferential_tariff_rate", "Preferential Tariff Rate under EAC (%)", value = 0),
  textInput("certificate_of_origin_number", "Certificate of Origin Number")
))

server = function(ui, server) {}

shinyApp(ui, server)
```

### 3. Non-Tariff Barrier Reporting Form

```{shinylive-r}
#| standalone: TRUE

ui <- fluidPage(
bslib::card(
  selectInput("barrier_type", "Type of Non-Tariff Barrier", 
              choices = c("Customs Procedures", "Technical Regulations", "Sanitary Measures", "Licensing Requirements", "Other")),
  selectInput("country", "Country Where Barrier was Encountered", 
              choices = c("Rwanda", "Kenya", "Uganda", "Tanzania", "Burundi", "South Sudan")),
  dateInput("date_encountered", "Date Encountered"),
  textAreaInput("barrier_description", "Detailed Description of the Barrier"),
  numericInput("estimated_cost", "Estimated Cost Impact (USD)", value = 0),
  textAreaInput("resolution_efforts", "Description of Resolution Efforts"),
  selectInput("status", "Current Status", 
              choices = c("Unresolved", "In Progress", "Resolved"))
))

server = function(ui, server) {}

shinyApp(ui, server)
```

Now, let's update our MongoDB setup script to include collections for these new forms:

```{r}
#| eval: false
#| echo: false
library(paws)
library(mongolite)

# AWS and MongoDB connection setup (as before)
# ...

# Create additional collections for free trade benefit data
product_origin <- mongo(collection = "product_origin", db = "rwandamarket", url = connection_string)
tariff_savings <- mongo(collection = "tariff_savings", db = "rwandamarket", url = connection_string)
non_tariff_barriers <- mongo(collection = "non_tariff_barriers", db = "rwandamarket", url = connection_string)

# Example: Insert a product origin record
product_origin$insert(
  data.frame(
    product_name = "Rwandan Mountain Coffee",
    hs_code = "0901.21",
    country_of_origin = "Rwanda",
    local_content_percentage = 95,
    manufacturing_process = "Locally grown, processed, and packaged in Rwanda",
    meets_origin_criteria = TRUE,
    date_submitted = Sys.Date()
  )
)

# Example: Insert a tariff savings record
tariff_savings$insert(
  data.frame(
    product_name = "Rwandan Mountain Coffee",
    hs_code = "0901.21",
    origin_country = "Rwanda",
    destination_country = "Kenya",
    shipment_value = 10000,
    standard_tariff_rate = 25,
    preferential_tariff_rate = 0,
    certificate_of_origin_number = "EAC-RW-2023-12345",
    date_of_shipment = Sys.Date()
  )
)

# Remember to close all connections when done
# ...
```

Now, let's create an R script to analyze the free trade benefits data:

```{r}
#| eval: false
#| echo: false
library(dplyr)
library(ggplot2)
library(lubridate)

# Assume we've loaded the data into dataframes: product_origin_data, tariff_savings_data, non_tariff_barrier_data

# Analyze tariff savings
total_savings <- tariff_savings_data %>%
  mutate(savings = shipment_value * (standard_tariff_rate - preferential_tariff_rate) / 100) %>%
  summarise(total_savings = sum(savings))

savings_by_product <- tariff_savings_data %>%
  mutate(savings = shipment_value * (standard_tariff_rate - preferential_tariff_rate) / 100) %>%
  group_by(product_name) %>%
  summarise(total_savings = sum(savings)) %>%
  arrange(desc(total_savings))

# Visualize tariff savings by product
ggplot(savings_by_product, aes(x = reorder(product_name, total_savings), y = total_savings)) +
  geom_bar(stat = "identity", fill = "#00A86B") +
  coord_flip() +
  labs(title = "Tariff Savings by Product", x = "Product", y = "Total Savings (USD)") +
  theme_minimal()

# Analyze non-tariff barriers
barriers_by_type <- non_tariff_barrier_data %>%
  group_by(barrier_type) %>%
  summarise(count = n(), total_cost_impact = sum(estimated_cost))

# Visualize non-tariff barriers
ggplot(barriers_by_type, aes(x = barrier_type, y = count, fill = total_cost_impact)) +
  geom_bar(stat = "identity") +
  scale_fill_gradient(low = "yellow", high = "red") +
  labs(title = "Non-Tariff Barriers by Type", x = "Barrier Type", y = "Count", fill = "Total Cost Impact (USD)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Analyze product origin compliance
origin_compliance <- product_origin_data %>%
  group_by(country_of_origin) %>%
  summarise(total_products = n(),
            compliant_products = sum(meets_origin_criteria),
            compliance_rate = compliant_products / total_products * 100)

# Print insights
cat("Total tariff savings:", sprintf("$%s", format(total_savings$total_savings, big.mark = ",")), "\n")
cat("Top 3 products by tariff savings:\n")
print(head(savings_by_product, 3))
cat("\nNon-tariff barriers summary:\n")
print(barriers_by_type)
cat("\nProduct origin compliance rates:\n")
print(origin_compliance)

# Recommendations based on analysis
cat("\nRecommendations:\n")
if (any(origin_compliance$compliance_rate < 95)) {
  cat("- Improve origin compliance for products from:", 
      origin_compliance$country_of_origin[origin_compliance$compliance_rate < 95], "\n")
}
if (nrow(barriers_by_type) > 0) {
  most_costly_barrier <- barriers_by_type %>% arrange(desc(total_cost_impact)) %>% slice(1)
  cat("- Focus on resolving", most_costly_barrier$barrier_type, 
      "barriers, which have the highest cost impact.\n")
}
top_saving_product <- savings_by_product$product_name[1]
cat("- Explore opportunities to increase trade of", top_saving_product, 
    "which provides the highest tariff savings.\n")
```

This system for documenting and analyzing free trade benefits will allow RwandaMarket to:

1.  Ensure compliance with Rules of Origin requirements for preferential tariff treatment.
2.  Track and quantify the financial benefits of utilizing free trade agreements.
3.  Identify and address non-tariff barriers that may be hindering trade.
4.  Optimize product sourcing and trade routes based on potential tariff savings.
5.  Provide data-driven insights for business strategy and government advocacy efforts.

To fully implement this system:

1.  Integrate these forms into the RwandaMarket website or internal systems.
2.  Set up automated data collection where possible (e.g., integrating with customs databases).
3.  Develop a dashboard to visualize key metrics related to free trade benefits.
4.  Implement regular reporting and analysis cycles to inform business decisions.
5.  Establish a process for acting on insights, such as addressing compliance issues or lobbying for resolution of persistent non-tariff barriers.

This comprehensive approach to tracking and analyzing free trade benefits will enable RwandaMarket to maximize the advantages of trade agreements, reduce costs, and streamline cross-border operations.
