---
title: "Operations Plan"
---

The RwandaMarket operations plan outlines our key processes and systems that enable us to efficiently source products from Rwanda, manage inventory, fulfill orders, and provide B2B services.

### Supply Chain Management

#### 1. Sourcing
- Direct partnerships with Rwandan artisans and cooperatives
- Regular sourcing trips to Rwanda (quarterly)
- Quality control checks at source

#### 2. Transportation
- Air freight for perishables and high-value items
- Sea freight for bulk, non-perishable goods
- Customs clearance process with dedicated partners

#### 3. Warehousing
- Central warehouse located in [PLACEHOLDER: Specific area in Nairobi]
- Climate-controlled storage for sensitive products
- RFID-based inventory tracking system

```{r}
#| echo: false
library(ggplot2)

## Supply chain process data
supply_chain_data <- data.frame(
  Stage = c("Sourcing", "Quality Check", "Transportation", "Customs Clearance", "Warehousing", "Distribution"),
  Time = c(14, 2, 7, 3, 1, 2)
)

## Create a horizontal bar chart of supply chain process
ggplot(supply_chain_data, aes(x = Time, y = reorder(Stage, -Time))) +
  geom_bar(stat = "identity", fill = "#00A86B") +
  theme_minimal() +
  labs(title = "Average Time per Supply Chain Stage",
       x = "Time (Days)",
       y = "") +
  geom_text(aes(label = paste(Time, "days")), hjust = -0.1)
```

### Inventory Control Systems

- R-based predictive analytics for demand forecasting
- Automated reorder points based on sales velocity and lead times
- Real-time inventory updates across e-commerce and physical store

### Order Fulfillment Process

1. Order received (e-commerce platform or in-store)
2. Order verification and payment processing
3. Inventory allocation
4. Picking and packing
5. Quality check
6. Shipping/delivery arrangement
7. Order tracking information sent to customer
8. Delivery confirmation and feedback request

### Customer Service Protocols

- Omnichannel support: Phone, email, chat, and social media
- 24/7 chatbot for basic inquiries and order tracking
- Escalation process for complex issues
- Regular team training on product knowledge and customer service skills

### Technology Infrastructure

#### E-commerce Platform
- Custom-built using R Shiny for frontend and Plumber for API
- Integrated with inventory management and CRM systems
- Mobile-responsive design

#### Data Analytics
- R-based analytics engine for business intelligence
- Real-time dashboards for key performance indicators
- Machine learning models for demand forecasting and customer segmentation

#### Security Measures
- End-to-end encryption for all transactions
- Regular security audits and penetration testing
- Compliance with data protection regulations in Kenya and Rwanda

```{r}
#| echo: false
library(ggplot2)

## Technology stack data
tech_stack <- data.frame(
  Category = c("Frontend", "Backend", "Database", "Analytics", "Security", "Cloud Infrastructure"),
  Technology = c("R Shiny", "R Plumber", "MongoDB", "R (tidyverse, caret)", "SSL/TLS, AWS Security", "AWS")
)

## Create a table-like visualization
ggplot(tech_stack, aes(x = 1, y = Category)) +
  geom_text(aes(label = Technology), hjust = 0, size = 3.5, position = position_nudge(x = 0.1)) +
  geom_text(aes(label = Category), hjust = 1, fontface = "bold", size = 3.5, position = position_nudge(x = -0.1)) +
  theme_void() +
  theme(axis.text.y = element_blank()) +
  labs(title = "RwandaMarket Technology Stack") +
  xlim(0, 2)
```

This operations plan ensures that RwandaMarket can efficiently manage its supply chain, inventory, order fulfillment, and customer service, all supported by a robust technology infrastructure.
