
---
title: "Optimization Documentation and Data Collection"
---

To fully optimize RwandaMarket's operations, we will collect and analyze data across various aspects of our business. This additional documentation and data collection will enable us to make data-driven decisions and continuously improve our processes.

## Supply Chain Optimization

1. Supplier Performance Tracking Form
   - Supplier Name
   - Order Fulfillment Rate
   - On-Time Delivery Rate
   - Product Quality Rating
   - Communication Responsiveness
   - Price Competitiveness

2. Logistics Performance Form
   - Shipping Method
   - Origin and Destination
   - Transit Time
   - Shipping Cost
   - Damage Rate
   - Customer Satisfaction with Delivery

3. Inventory Turnover Tracking
   - Product SKU
   - Initial Stock Level
   - Sales Volume
   - Restocking Frequency
   - Storage Costs

## Customer Experience Optimization

1. Customer Feedback Form
   - Overall Satisfaction Rating
   - Product Quality Rating
   - Delivery Experience Rating
   - Customer Service Rating
   - Website Usability Rating
   - Open-ended Feedback

2. Website Analytics Integration
   - Page Views
   - Time on Site
   - Bounce Rate
   - Conversion Rate
   - Cart Abandonment Rate
   - Search Terms Used

3. Customer Support Ticket Tracking
   - Ticket Category
   - Resolution Time
   - Customer Satisfaction with Resolution
   - Recurring Issues Identification

## Business Operations Optimization

1. Employee Productivity Tracking
   - Employee ID
   - Department
   - Tasks Completed
   - Time Spent on Tasks
   - Quality of Work Rating

2. Financial Performance Metrics
   - Revenue by Product Category
   - Gross Margin by Product
   - Customer Acquisition Cost
   - Customer Lifetime Value
   - Operating Expenses Breakdown

3. Marketing Campaign Effectiveness
   - Campaign ID
   - Channel (e.g., Social Media, Email, PPC)
   - Reach
   - Engagement Rate
   - Conversion Rate
   - Return on Ad Spend (ROAS)

## B2B Services Optimization

1. Trade Facilitation Service Feedback
   - Service Type
   - Completion Time
   - Cost Effectiveness Rating
   - Problem Resolution Efficiency
   - Overall Satisfaction

2. Cross-Border Trade Analytics
   - Trade Volume by Country
   - Most Popular Product Categories
   - Average Customs Clearance Time
   - Duty and Tax Payments
   - Trade Compliance Issues Encountered

Now, let's create a sample form for Supplier Performance Tracking and update our database schema to accommodate these new data points:

```{r}
#| echo: false
library(shiny)

supplier_performance_form <- fluidPage(
  textInput("supplier_name", "Supplier Name"),
  numericInput("order_fulfillment_rate", "Order Fulfillment Rate (%)", value = 0, min = 0, max = 100),
  numericInput("on_time_delivery_rate", "On-Time Delivery Rate (%)", value = 0, min = 0, max = 100),
  sliderInput("product_quality_rating", "Product Quality Rating", min = 1, max = 5, value = 3, step = 0.5),
  sliderInput("communication_responsiveness", "Communication Responsiveness", min = 1, max = 5, value = 3, step = 0.5),
  sliderInput("price_competitiveness", "Price Competitiveness", min = 1, max = 5, value = 3, step = 0.5)
)

fluidPage(
  h2("Supplier Performance Tracking Form"),
  supplier_performance_form
)
```

Now, let's update our MongoDB setup script to include collections for these new data points:

```{r}
#| eval: false
#| echo: false
library(paws)
library(mongolite)

# AWS and MongoDB connection setup (as before)
# ...

# Create additional collections for optimization data
supplier_performance <- mongo(collection = "supplier_performance", db = "rwandamarket", url = connection_string)
logistics_performance <- mongo(collection = "logistics_performance", db = "rwandamarket", url = connection_string)
inventory_turnover <- mongo(collection = "inventory_turnover", db = "rwandamarket", url = connection_string)
customer_feedback <- mongo(collection = "customer_feedback", db = "rwandamarket", url = connection_string)
website_analytics <- mongo(collection = "website_analytics", db = "rwandamarket", url = connection_string)
support_tickets <- mongo(collection = "support_tickets", db = "rwandamarket", url = connection_string)
employee_productivity <- mongo(collection = "employee_productivity", db = "rwandamarket", url = connection_string)
financial_metrics <- mongo(collection = "financial_metrics", db = "rwandamarket", url = connection_string)
marketing_campaigns <- mongo(collection = "marketing_campaigns", db = "rwandamarket", url = connection_string)
trade_facilitation_feedback <- mongo(collection = "trade_facilitation_feedback", db = "rwandamarket", url = connection_string)
cross_border_analytics <- mongo(collection = "cross_border_analytics", db = "rwandamarket", url = connection_string)

# Example: Insert a supplier performance record
supplier_performance$insert(
  data.frame(
    supplier_name = "Rwanda Coffees Ltd",
    order_fulfillment_rate = 95,
    on_time_delivery_rate = 92,
    product_quality_rating = 4.5,
    communication_responsiveness = 4,
    price_competitiveness = 3.5,
    date = Sys.Date()
  )
)

# Example: Query supplier performance
result <- supplier_performance$find('{"supplier_name": "Rwanda Coffees Ltd"}')
print(result)

# Remember to close all connections when done
# ...
```

To leverage this data for optimization, we can create R scripts that perform analysis and generate insights. Here's an example of how we might analyze supplier performance:

```{r}
#| eval: false
#| echo: false
library(dplyr)
library(ggplot2)

# Assuming we've queried all supplier performance data into a dataframe called 'supplier_data'

# Calculate average performance metrics for each supplier
supplier_summary <- supplier_data %>%
  group_by(supplier_name) %>%
  summarize(
    avg_fulfillment_rate = mean(order_fulfillment_rate),
    avg_delivery_rate = mean(on_time_delivery_rate),
    avg_quality_rating = mean(product_quality_rating),
    avg_responsiveness = mean(communication_responsiveness),
    avg_price_competitiveness = mean(price_competitiveness)
  )

# Identify top performing suppliers
top_suppliers <- supplier_summary %>%
  arrange(desc(avg_fulfillment_rate)) %>%
  head(5)

# Visualize supplier performance
ggplot(supplier_summary, aes(x = avg_fulfillment_rate, y = avg_quality_rating, color = supplier_name)) +
  geom_point(size = 3) +
  labs(title = "Supplier Performance: Fulfillment Rate vs Quality Rating",
       x = "Average Order Fulfillment Rate",
       y = "Average Product Quality Rating") +
  theme_minimal()

# Output insights
cat("Top 5 suppliers by order fulfillment rate:\n")
print(top_suppliers)

# Identify areas for improvement
low_performing_areas <- supplier_summary %>%
  filter(avg_fulfillment_rate < 90 | avg_delivery_rate < 90 | avg_quality_rating < 4)

cat("\nSuppliers needing improvement:\n")
print(low_performing_areas)
```

This expanded documentation and data collection system allows RwandaMarket to:

1. Track and analyze supplier performance to optimize the supply chain
2. Monitor logistics performance to improve delivery times and reduce costs
3. Optimize inventory levels based on turnover rates
4. Improve customer experience through detailed feedback analysis
5. Enhance website performance using analytics data
6. Streamline customer support processes
7. Monitor and improve employee productivity
8. Track financial performance at a granular level
9. Measure and optimize marketing campaign effectiveness
10. Continuously improve B2B services based on feedback and analytics

To fully implement this optimization system:

1. Create individual forms in Quarto for each data collection point
2. Set up automated data collection where possible (e.g., website analytics)
3. Develop a dashboard in R Shiny to visualize key performance indicators
4. Create scheduled R scripts to perform regular analysis and generate reports
5. Implement a system for alerts when metrics fall below certain thresholds
6. Regularly review and adjust optimization strategies based on the insights generated

This comprehensive approach to data collection and analysis will enable RwandaMarket to continuously optimize its operations, improving efficiency, customer satisfaction, and overall business performance.

