---
title: "Products and Services"
---

RwandaMarket offers a unique blend of B2C products and B2B services, all centered around authentic Rwandan goods and cross-border trade facilitation.

### B2C Product Categories

#### 1. Coffee and Tea
- Single-origin Rwandan coffee beans
- Specialty tea blends
- Coffee and tea accessories

#### 2. Handicrafts
- Traditional Rwandan baskets (Agaseke)
- Wood carvings and sculptures
- Pottery and ceramics

#### 3. Textiles
- Handwoven fabrics
- Traditional and modern clothing items
- Home textiles (curtains, tablecloths, etc.)

#### 4. Jewelry
- Handcrafted jewelry using local materials
- Traditional and contemporary designs

#### 5. Art
- Paintings and prints by Rwandan artists
- Imigongo (cow dung art)
- Contemporary sculptures

```{r}
#| echo: false
library(ggplot2)

## Product category data
category_data <- data.frame(
  Category = c("Coffee & Tea", "Handicrafts", "Textiles", "Jewelry", "Art"),
  Percentage = c(30, 25, 20, 15, 10)
)

## Create a pie chart of product categories
ggplot(category_data, aes(x = "", y = Percentage, fill = Category)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y", start = 0) +
  theme_void() +
  labs(title = "B2C Product Category Distribution") +
  scale_fill_brewer(palette = "Set3") +
  geom_text(aes(label = paste0(Percentage, "%")), position = position_stack(vjust = 0.5))
```

### B2B Services

#### 1. Cross-Border Trade Facilitation
- Customs documentation assistance
- Logistics optimization
- Regulatory compliance guidance

#### 2. Market Intelligence
- Consumer trend analysis
- Competitive landscape mapping
- Market entry strategy consulting

#### 3. Supply Chain Analytics
- Demand forecasting
- Inventory optimization
- Route planning and optimization

#### 4. Blockchain-Enabled Product Authentication
- End-to-end supply chain tracking
- Counterfeit protection
- Consumer trust building

### Pricing Strategy

#### B2C Pricing
Our B2C pricing strategy aims to position our products as premium, authentic Rwandan goods. Prices are set to reflect the quality and uniqueness of the items, while remaining competitive in the Nairobi market.

[PLACEHOLDER: Specific pricing examples]

#### B2B Pricing
Our B2B services are priced using a tiered model, with basic packages for small businesses and more comprehensive solutions for larger enterprises. We also offer customized pricing for bespoke services.

[PLACEHOLDER: B2B pricing tier details]

### Product Sourcing and Quality Control

#### Sourcing Process
1. Direct partnerships with Rwandan cooperatives and artisans
2. Regular sourcing trips to Rwanda
3. Stringent supplier vetting process

#### Quality Control Measures
1. Initial quality check at source in Rwanda
2. Secondary inspection upon arrival at our Nairobi warehouse
3. Random batch testing for consistency
4. Customer feedback integration for continuous improvement

```{r}
#| echo: false
library(ggplot2)

## Quality control process data
qc_data <- data.frame(
  Stage = c("Source Inspection", "Arrival Check", "Batch Testing", "Customer Feedback"),
  Importance = c(40, 30, 20, 10)
)

## Create a horizontal bar chart of quality control process
ggplot(qc_data, aes(x = Importance, y = reorder(Stage, Importance))) +
  geom_bar(stat = "identity", fill = "#00A86B") +
  theme_minimal() +
  labs(title = "Quality Control Process Weightage",
       x = "Importance (%)",
       y = "") +
  geom_text(aes(label = paste0(Importance, "%")), hjust = -0.1)
```

Our comprehensive range of products and services, coupled with our commitment to quality and authenticity, positions RwandaMarket as a unique player in the East African market.

